---
title: "Assignment for Data Science - Practical Machine Learning"
author: "Wei Jiang"
date: "Saturday, February 21, 2015"
output: html_document
---

## Overview

[HAR](http://groupware.les.inf.puc-rio.br/har) has collected data about personal activities. Here we are trying to use this data to predict person activity manner, the manner they do their exercises, and cross-validate with testing data. The training set will be splitted into two sets: one set (60% of data) for training, one set (40% of data) for cross-validation. Finally we will use the best model to predict on a testing set (20 observations).

## Data

First we download and read the data, and check summary:

```{r, cache=TRUE, results='hide'}
setwd=("d:/R/RStudio/coursera/8.Practical_machine_learning/ass1")
if (!file.exists("pml-training.csv")) {
    download.file(url="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", destfile="pml-training.csv")
}
if (!file.exists("pml-testing.csv")) {
    download.file(url="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", destfile="pml-testing.csv")
}

original_data <- read.csv("pml-training.csv", as.is = TRUE)
dim(original_data)
dim(original_data)
summary(original_data)
head(original_data)
```

Remove columns with too many NAs. Then prepare the training/testing data (60%/40%), and the pml-testing.csv is for predicting.

```{r}
library(dplyr)
original_data <- select(original_data, -(raw_timestamp_part_1:raw_timestamp_part_2))
original_data <- select(original_data, -(max_roll_belt:max_picth_belt))
original_data <- select(original_data, -c(min_roll_belt,min_pitch_belt,amplitude_roll_belt,amplitude_pitch_belt,var_total_accel_belt:var_yaw_belt))
original_data <- select(original_data, -(var_accel_arm:var_yaw_arm))
original_data <- select(original_data, -(max_roll_arm:amplitude_yaw_arm))
original_data <- select(original_data, -c(max_roll_dumbbell,max_picth_dumbbell,min_roll_dumbbell,min_pitch_dumbbell,amplitude_roll_dumbbell,amplitude_pitch_dumbbell,var_accel_dumbbell:var_yaw_dumbbell,max_roll_forearm,max_picth_forearm,min_roll_forearm,min_pitch_forearm,amplitude_roll_forearm,amplitude_pitch_forearm))
original_data <- select(original_data, -(var_accel_forearm:var_yaw_forearm))
original_data <- select(original_data, -(kurtosis_roll_belt:amplitude_yaw_belt))
original_data <- select(original_data, -(kurtosis_roll_arm:skewness_yaw_arm))
original_data <- select(original_data, -(kurtosis_roll_dumbbell:amplitude_yaw_dumbbell))
original_data <- select(original_data, -(kurtosis_roll_forearm:amplitude_yaw_forearm))
original_data <- select(original_data, -c(X,user_name))

## library(lubridate)
## original_data$cvtd_timestamp <- mdy_hm(original_data$cvtd_timestamp)
original_data$classe <- as.factor(original_data$classe)
original_data <- subset(original_data, !is.na(cvtd_timestamp))

library(caret)
inTrain <- createDataPartition(y=original_data$classe, p=0.6, list=FALSE)
training <- original_data[inTrain,]  ## 11776*58
testing <- original_data[-inTrain,]
predicting <- read.csv("pml-testing.csv", as.is = TRUE)
```

## Analysis and results

Set up a model with random forest:

```{r}
set.seed(32343)
modelFit <- train(classe~.,data=training,method="rf", prox=TRUE)
print(modelFit$finalModel)
pred <- predict(modelFit, testing); testing$classe_right <- pred==testing$classe
```

Now set up a model with rpart:

```{r}
modelFit2 <- train(classe~., method="rpart", data=training)

print(modelFit2$finalModel)
library(rattle)
fancyRpartPlot(modelFit2$finalModel)
pred2 <- predict(modelFit2, newdata=testing); testing$classe_right2 <- pred2==testing$classe

```

We can tell first model got better accuracy:

```{r}
modelFit
modelFit2
```

We can verify first model "rf" against testing set:

```{r}
## testing$classe_right
table(pred, testing$classe)
```

Then the second model "rpart":

```{r}
## testing$classe_right2
table(pred2,testing$classe)
```

Clearly model 1 (random forest) got much better performance.

Finally we use model 1 on predicting data set:

```{r}
pred3 <- predict(modelFit, newdata=predicting)
pred3
```

\newpage

## Supporting materials

### Data
Data comes from [Human Activity Recognition](http://groupware.les.inf.puc-rio.br/har).

### Code and figures

N/A.

### Environment and software

This report was created through "Knit PDF" in RStudio, on Windows 7 Premium (64bit) Chinese version.

Following software were used:

1. R i386 3.1.2
2. R Studio 0.98.1091
3. Knitr_1.9
4. rmarkdown_0.5.1
5. dplyr_0.4.1
6. lubridate_1.3.3
7. caret_6.0-41
8. randomForest_4.6-10
9. rpart_4.1-9

### Contact

If you have any issues/concerns, please feel free to [contact me](mailto:jiangwei49@yahoo.com).
